Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-06-05 LaTeX_paper/paper.tex
finish latex section 3.2 (GCL)

\subsection{Solving Jigsaw Puzzles By The Graph Connection Laplacian~\cite{GCL}}
This algorithm falls in the “binary comparison” category~\ref{document:comparator}.
And can be used to understand the strength and weaknesses
of this approach.\newline
The main benefit of this approach is speed,  having a binary comparison allows
some specific optimization, in particular the use of some graph theory techniques.\newline
The  algorithm has a time complexity of ruffly \(O(N^2)\). Which is in line with the theoretical
minimum for jigsaw puzzle solving, according to the study:
\footnotesize{“No easy puzzles: Hardness results for jigsaw puzzles~\cite{ON2Claim}”}.

>>>>

\subsection{Solving Jigsaw Puzzles By The Graph Connection Laplacian~\cite{GCL}}
This algorithm falls in the “binary comparison” category~\ref{document:comparator}.
And can be used to understand the strength and weaknesses
of this approach.\newline
The main benefit of this approach is speed,  having a binary comparison allows
some specific optimization, in particular the use of some graph theory techniques.\newline
The  algorithm has a time complexity of ruffly \(O(N^2)\). Which is in line with the theoretical
minimum for jigsaw puzzle solving, according to the study:
“No easy puzzles: Hardness results for jigsaw puzzles~\cite{ON2Claim}”.\newline
The negative aspect might be the accuracy, since by using only two states
(match or not match) some informations are lost, compared to a non binary comparison.
To quantify accuracy the paper used the “neighbors comparison” metric,
which “calculates the percentage of pairs of image patches that are matched correctly”.\newline
Is important to note that the discussed algorithm works with 
digital puzzles~\ref{fig:figure_digital_puzzle}, and this gives it the advantage of having more precise data.\newline
Whether this algorithm could work with a real world puzzle~\ref{fig:figure_real_puzzle} will be discussed in section DOTO INSERT RFERENCE.
